A multi-dimensional extension of the Lightweight Temporary Compression method

### 2018-10-01 paper.tex
fix tex
fill tables for result

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

\section{Results}
\todo{ result table ?}
\subsection{Data sets}
\todo{ my data set}

@@

\section*{Acknowledgement}

>>>>

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\usepackage{algpseudocode}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

\section{Results}
\todo{ result table ?}
\subsection{Experiment 1: Pilot tests on Computer}
\begin{itemize}
    \item Data set: 5-times bicep curl which includes 613 data; 
                    Mohammad Lateral bicep curl which include 41428 data; 
                    All data is collected from Neblina, with 50Hz sampling of Sensors.
    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
    \item Result: Result shows in table.
    \item Conclution: 
\end{itemize}

\subsection{Experiment 1: energy reduction on the Neblina}
\begin{itemize}
    \item Data set: 5-times bicep curl which includes 613 data; 
                    Mohammad Lateral bicep curl which include 41428 data; 
                    All data is collected from Neblina, with 50Hz sampling of Sensors.
    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
    \item Result: Result shows in table.
    \item Conclution: 
\end{itemize}

@@

\section*{Acknowledgement}
\begin{table}[]
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    \multicolumn{9}{|l|}{Dimension 2}                                                                                                                         \\ \hline
    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
    Epsilon                & 100          & 100/sqrt(2)     & 100         & 100/sqrt(2)     & 100        & 100/sqrt(2)       & 100        & 100/sqrt(2)       \\ \hline
    Max Error              & 127.63       & 94.46           & 99.63       & 70.47           & 140.70     & 99.73             & 99.99      & 70.71             \\ \hline
    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%         & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ \hline
    Max memory Usage(peak) & 80B          & 80B             & 432B        & 240B            & 80B        & 80B               & 2.1KB      & 1.3KB             \\ \hline
    processing time Usage  & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms         & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
    \end{tabular}
\end{table}

\begin{table}[]
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    \multicolumn{9}{|l|}{Dimension 3}                                                                                                                         \\ \hline
    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
    Epsilon                & 100          & 100/sqrt(3)     & 100         & 100/sqrt(3)     & 100        & 100/sqrt(3)       & 100        & 100/sqrt(3)       \\ \hline
    Max Error              & 141.66       & 85.40           & 99.94       & 56.89           & 168.95     & 97.01             & 99.99      & 57.73             \\ \hline
    Compression Radio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%          & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\ \hline
    Max memory Usage(peak) & 112B         & 112B            & 384B        & 256B            & 112B       & 112B              & 4.9KB      & 3.0KB             \\ \hline
    processing time Usage  & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms         & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
    \end{tabular}
\end{table}
